Curve counting in genus one: elliptic singularities {\it \&} relative geometry

### 2019-06-28 EllipticSingularitiesSplitting.tex
minor changes

\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including \tred{Francesca Carocci,} Davesh Maulik, Jonathan Wise, and [other people]. Important aspects of this work were completed while L.B. and N.N. were visiting MIT in Spring 2018 and the University of Cambridge in Winter 2019, and we thank these institutions for their hospitality. \tred{L.B. would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, the MSRI program ''Enumerative Geometry beyond Numbers``, and MPIM-Bonn for support.}

>>>>

\subsection*{Acknowledgements} We have benefited from fruitful conversations with friends and colleagues, including \tred{Francesca Carocci, Cristina Manolache,} Davesh Maulik, Jonathan Wise, and [other people]. Important aspects of this work were completed while L.B. and N.N. were visiting MIT in Spring 2018 and the University of Cambridge in Winter 2019, and we thank these institutions for their hospitality. \tred{L.B. would like to thank Imperial College London, the LSGNT, the Royal Society, 3CinG, the MSRI program ''Enumerative Geometry beyond Numbers``, and MPIM-Bonn for support.}
